---
title: "main_analysis_EU"
author: "Tan Jing Ling"
date: "3/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Replication Code for Dataset with EU ETS Price Points

# Import Carbon Pricing Dataset
Obtained from the World Bank's Carbon Pricing Dashboard 
```{r}
# Set working directory
#setwd("~/your_working_directory")

# Import file
library(readr)
cppeu <- read_csv("Data files/CPP_ WithEU.csv")
#Do remember to change the file path 

#Convert Country Name to iso3c 3-letter code
library(countrycode)
cppeu$ifs <- countryname(cppeu$Country, destination = 'iso3c')
```

# Import and Modify CEPII Dataset
```{r}
# Import file
library(readr)
dist_cepii <- read_csv("Data files/dist_cepii.csv")
#Do remember to change the file path 

##### Modifications

# Keep only immediate neighbours
dist2 <- subset(dist_cepii, subset = (contig == 1 ))

# Remove dyadic duplicates of Country A-B / Country B-A
dist2$compare <- ifelse (dist2$iso_o > dist2$iso_d, 
                         paste(dist2$iso_o, dist2$iso_d, sep = "_"),
                         paste(dist2$iso_d, dist2$iso_o, sep = "_"))
library(dplyr)
dist3 <- distinct(dist2, compare, .keep_all = TRUE) 
```

# Import and Modify World Bank Control Variable Data
```{r}
library(readr)
WB <- read_csv("Data files/WBdata2.csv")
#Do remember to change the file path 

# Reshape data from Wide to Long Format (Add years to countries)
library(tidyr)
WB2 <- gather(data = WB, key = "Year", value = "Value", 5:34) 
table(WB2$`Series Name`)

#Split data from Long to Wide (split variables into columns)
library(dplyr)
WB2 %>% separate(`Series Name`, 
c("GDP (constant 2015 US$)", 
  "GDP per capita (constant 2015 US$)", "Trade (% of GDP)",
  "Exports of goods and services (% of GDP)",
  "Coal rents (% of GDP)",
  "CO2 emissions (metric tons per capita)",
  "Energy intensity level of primary energy (MJ/$2011 PPP GDP)",
  "Energy use (kg of oil equivalent per capita)", 
  "Methane emissions in energy sector (thousand metric tons of CO2 equivalent)",
  "Nitrous oxide emissions in energy sector (thousand metric tons of CO2 equivalent)",
  "Renewable energy consumption (% of total final energy consumption)",
  "Energy imports, net (% of energy use)", 
  "Population, total",
  "Total greenhouse gas emissions (kt of CO2 equivalent)",
  "Electric power consumption (kWh per capita)",
  "Oil rents (% of GDP)",
  "Total natural resources rents (% of GDP)",
  "Natural gas rents (% of GDP)",
  "Fossil fuel energy consumption (% of total)", NA))

library(reshape2)
WB3 <- dcast(WB2, `Country Name` + `Country Code` + `Year`~ `Series Name`, value.var = "Value")
```

# Merge CPP and CEPII data
```{r}
cppeu <- merge(x = cppeu, y = dist3, by.x = "ifs", by.y = "iso_o", all.x = TRUE) 

# Reshape data by Country and Year
cppeu2 <- gather(data = cppeu, key = "Year", value = "Price", 8:39) 
cppeu2$id <- paste(cppeu2$ifs, cppeu2$Year, sep="_")

# Create Variable with country-year of neighbours
cppeu2$iso_d_year <- ifelse(cppeu2$iso_d == "", NA, 
paste(cppeu2$iso_d, cppeu2$Year, sep="_"))
```

# Create new dataframe with iso_d_year prices (Neighbour, Country-Year Prices)
```{r}
isodcppeu <- merge(x= cppeu, y = dist3, by.x = "ifs", by.y = "iso_d", all = TRUE)
isodcppeu2 <- gather(data = isodcppeu, key = "Year", value = "Price", 8:39) 
isodcppeu2$iso_d_year <- paste(isodcppeu2$ifs, isodcppeu2$Year, sep="_")
isodcppeu3 <- data.frame(iso_d_year = as.character(isodcppeu2$iso_d_year), iso_d_price = as.numeric(isodcppeu2$Price))
isodcppeu4 <- distinct(isodcppeu3, iso_d_year, .keep_all = TRUE)
isodcppeu4$iso_d_adopt <- ifelse(isodcppeu4$iso_d_price > 0, 1, 0)

# Merge iso_d prices to main dataset
cppeu3 <- merge(x = cppeu2, y = isodcppeu4, by = "iso_d_year", all.x = TRUE)
```

# Obtain mean, min, max 
For iso_d_price (Neighbour Price), Regional Price, and Global Price
```{r warning = FALSE} 
# Create neighbour df to isolate neighbouring mean, max, min prices
neighbour <- cppeu3 %>% group_by(id) %>% 
    summarise(mean_iso_d = mean(iso_d_price, na.rm =TRUE), 
              min_iso_d = min(iso_d_price, na.rm = TRUE), 
              max_iso_d = max(iso_d_price, na.rm = TRUE),
              mean_iso_d_adopt = mean(iso_d_adopt, na.rm =TRUE),)

cppeu3$regionyear <- paste(cppeu3$Region, cppeu3$Year, sep="_")

# Create regional df to isolate regional mean, max, min prices

regional <- cppeu3 %>% group_by(regionyear) %>% 
    summarise(mean_region = mean(iso_d_price, na.rm =TRUE), 
              min_region = min(iso_d_price, na.rm = TRUE), 
              max_region = max(iso_d_price, na.rm = TRUE),
              mean_region_adopt = mean(iso_d_adopt, na.rm=TRUE))

cppeu3$NumberCPP <- ifelse(cppeu3$Price > 0, 1, 0)

# Create glaobl df to isolate global mean, max, min prices

global <- cppeu3 %>% group_by(Year) %>% 
    summarise(mean_global = mean(Price, na.rm =TRUE),
              mean_global_adopt = mean(NumberCPP, na.rm = TRUE))

# Merge back into main df

cppeu4 <- merge(x = cppeu3, y = neighbour, by = "id", all.x = TRUE)

cppeu4.1 <- merge(x = cppeu4, y = regional, by = "regionyear", all.x = TRUE)

cppeu4.2 <- merge(x = cppeu4.1, y = global, by = "Year", all.x = TRUE)

# Remove NaN and infinite values

cppeu4.2 <- do.call(data.frame,                   
                   lapply(cppeu4.2,
                          function(x) replace(x, is.infinite(x), NA)))

cppeu4.2 <- do.call(data.frame,                   
                   lapply(cppeu4.2,
                          function(x) replace(x, is.nan(x), NA)))

cppeu5 <- distinct(cppeu4.2, id, .keep_all = TRUE)
```

# Tidying World Bank Dataset
```{r}
table(WB2$`Series Name`)

# Renaming variables

names(WB3)[names(WB3) == "Country Name"] <- "Country"
names(WB3)[names(WB3) == "Country Code"] <- "ifs" 
names(WB3)[names(WB3) == "GDP (constant 2015 US$)"] <- "GDP"
names(WB3)[names(WB3) == "CO2 emissions (metric tons per capita)"] <- "CO2_PC"
names(WB3)[names(WB3) == "Electric power consumption (kWh per capita)"] <- "electricity_PC"
names(WB3)[names(WB3) == "Energy imports, net (% of energy use)"] <- "energy_imports"
names(WB3)[names(WB3) == "Energy intensity level of primary energy (MJ/$2011 PPP GDP)"] <- "energy_intensity"
names(WB3)[names(WB3) == "Energy use (kg of oil equivalent per capita)"] <- "energy_use_pc"
names(WB3)[names(WB3) == "Renewable energy consumption (% of total final energy consumption)"] <- "renewable"
names(WB3)[names(WB3) == "Trade (% of GDP)"] <- "trade_gdp"
names(WB3)[names(WB3) == "GDP per capita (constant 2015 US$)"] <- "GDP_PC"
names(WB3)[names(WB3) == "Exports of goods and services (% of GDP)"] <- "exports_gdp"
names(WB3)[names(WB3) == "Coal rents (% of GDP)"] <- "coal_gdp"
names(WB3)[names(WB3) == "Fossil fuel energy consumption (% of total)"] <- "fossil_fuel"
names(WB3)[names(WB3) == "Methane emissions in energy sector (thousand metric tons of CO2 equivalent)"] <- "methane_emissions"
names(WB3)[names(WB3) == "Natural gas rents (% of GDP)"] <- "natural_gas_gdp"
names(WB3)[names(WB3) == "Nitrous oxide emissions in energy sector (thousand metric tons of CO2 equivalent)"] <- "nitrous_oxide"
names(WB3)[names(WB3) == "Oil rents (% of GDP)"] <- "oil_rent_gdp"
names(WB3)[names(WB3) == "Population, total"] <- "population"
names(WB3)[names(WB3) == "Total greenhouse gas emissions (kt of CO2 equivalent)"] <- "greenhouse_emissions"
names(WB3)[names(WB3) == "Total natural resources rents (% of GDP)"] <- "natural_resource_gdp"
```

# Merging World Bank Data to CPP with Mofidications
```{r warning = FALSE}
cppeu6 <- merge(x = cppeu5, y = WB3, by = c("ifs","Year"), all.x = TRUE) 

# Creating log variables (Note: not all log values are used)

# Divide GDP by 1000 and log 
cppeu6$GDP <- as.numeric(cppeu6$GDP)
cppeu6$GDPmillions <- cppeu6$GDP/1000000
cppeu6$logGDPmillions <- log(cppeu6$GDPmillions)

# Divide GDP_PC by 1000 and log
cppeu6$GDP_PC <- as.numeric(cppeu6$GDP_PC)
cppeu6$GDP_PCthousands <- cppeu6$GDP_PC/1000
cppeu6$logGDP_PCthousands <- log(cppeu6$GDP_PCthousands)

# Log energy use
cppeu6$energy_use_pc<- as.numeric(cppeu6$energy_use_pc)
cppeu6$logenergy_use_pc <- log(cppeu6$energy_use_pc)

# Log energy intensity
cppeu6$energy_intensity<- as.numeric(cppeu6$energy_intensity)
cppeu6$logenergy_intensity <- log(cppeu6$energy_intensity)

# Log coal
cppeu6$coal_gdp <- as.numeric(cppeu6$coal_gdp)
cppeu6$logcoal_gdp <- log(cppeu6$coal_gdp)

# Log CO2
cppeu6$CO2_PC <- as.numeric(cppeu6$CO2_PC)
cppeu6$logCO2_PC <- log(cppeu6$CO2_PC)

# Log Renewable
cppeu6$renewable <- as.numeric(cppeu6$renewable)
cppeu6$logrenewable <- log(cppeu6$renewable)

# Log Exports
cppeu6$exports_gdp <- as.numeric(cppeu6$exports_gdp)
cppeu6$logexports_gdp <- log(cppeu6$exports_gdp)

# Log Trade
cppeu6$trade_gdp <- as.numeric(cppeu6$trade_gdp)
cppeu6$logtrade_gdp<- log(cppeu6$trade_gdp)

# Log Fossil Fuel 
cppeu6$fossil_fuel <- as.numeric(cppeu6$fossil_fuel)
cppeu6$logfossil_fuel<- log(cppeu6$fossil_fuel)

# Log electricity
cppeu6$electricity_PC <- as.numeric(cppeu6$electricity_PC)
cppeu6$logelectricity_PC<- log(cppeu6$electricity_PC)

# Log Greenhouse Emissions
cppeu6$greenhouse_emissions <- as.numeric(cppeu6$greenhouse_emissions)
cppeu6$loggreenhouse_emissions<- log(cppeu6$greenhouse_emissions)

# Log nitrous_oxide
cppeu6$nitrous_oxide <- as.numeric(cppeu6$nitrous_oxide)
cppeu6$lognitrous_oxide<- log(cppeu6$nitrous_oxide)

# Log Methane
cppeu6$methane_emissions <- as.numeric(cppeu6$methane_emissions)
cppeu6$logmethane_emissions<- log(cppeu6$methane_emissions)

# Log Natural Gas Rents (% GDP)
cppeu6$natural_gas_gdp <- as.numeric(cppeu6$natural_gas_gdp)
cppeu6$lognatural_gas_gdp <- log(cppeu6$natural_gas_gdp)

# Log Natural Resources
cppeu6$natural_resource_gdp <- as.numeric(cppeu6$natural_resource_gdp)
cppeu6$lognatural_resource_gdp <- log(cppeu6$natural_resource_gdp)

# Log Population
cppeu6$population <- as.numeric(cppeu6$population)
cppeu6$populationby1000 <- cppeu6$population/1000
cppeu6$logpopulation <- log(cppeu6$population)
cppeu6$logpopulationby1000 <- log(cppeu6$populationby1000)

# Log oil rents
cppeu6$oil_rent_gdp <- as.numeric(cppeu6$oil_rent_gdp)
cppeu6$logoil_rent_gdp <- log(cppeu6$oil_rent_gdp)

# Log Energy Imports
cppeu6$energy_imports <- as.numeric(cppeu6$energy_imports)
cppeu6$logenergy_imports <- log(cppeu6$energy_imports)

# Removing NaN and infinite values as a result of logging

cppeu6 <- do.call(data.frame,                   
                   lapply(cppeu6,
                          function(x) replace(x, is.infinite(x), NA)))

cppeu6 <- do.call(data.frame,                   
                   lapply(cppeu6,
                          function(x) replace(x, is.nan(x), NA)))
```

#Importing DPI Dataset
For checks and balance control variable
```{r}
DPI <- read_csv("Data files/DPI.csv")
#Do remember to change the file path 
```

#Modifications to DPI Dataset + Merging
```{r}
# Modifications to DPI Dataset
DPI$checks2 = DPI$checks_lax
DPI$checks2[DPI$checks2 < 1] = NA

# Rename variables to be consistent with the other dataframes
names(DPI)[names(DPI) == "year"] <- "Year"

# Merging 
cppeu7 <- merge(x = cppeu6, y = DPI, by = c("ifs","Year"), all.x = TRUE) 
```

# Baseline Multiple Regressions 

```{r }
library(plm)
library(stargazer)

base_eu_mean<- plm(Price~mean_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

base_eu_max<- plm(Price~max_iso_d + mean_region + mean_global + logGDPmillions +logGDP_PCthousands  + renewable + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2, data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

base_eu_min<- plm(Price~min_iso_d  + mean_region + mean_global + logGDPmillions + logGDP_PCthousands  + renewable + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2, data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

EUbase <- stargazer(base_eu_mean, base_eu_max, base_eu_min,
          type = "html",
          title = "EU Model - Neighbourhood Effect on Price of CPP",
          dep.var.labels = "CPP Price in Constant US Dollars",
          column.labels = c("Mean Price", "Maximum Price", "Minimum Price"),
          covariate.labels = c("Mean Carbon Price, Neighbours", "Maximum Carbon Price, Neighbours", "Minimum Carbon Price, Neighbours", "Regional Mean Price","Global Mean Price by Year", "GDP (Millions, Logged)", "GDP Per Capita (Thousands, Logged)", "Renewable Energy Consumption (% of total)",  "Trade (% of GDP)", "CO2 emissions (Metric Tonnes Per Capita, Logged )","Natural Resource Rents (% of GDP)", "Population (Thousands, Logged )", "Check and Balances (DPI Index)"),
          style = "apsr", notes.append = TRUE, notes.align = "c",
          notes.label = 'Notes:',
          notes ="\\parbox[t]{\\textwidth}{Carbon Prices are those of a country's Immediate Neighbours}",
          no.space=TRUE,
          out = "EUbase.htm")

# Note that the lines above create a html file in your working directory with the regression output
```

# Random Effects and Hausman Test
```{r}
library(plm)

base_eu_re<- plm(Price~mean_iso_d + logGDPmillions + logGDP_PCthousands + logenergy_intensity + logrenewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 + mean_region + mean_global, data = cppeu7, index = "ifs", model = "random", na.action=na.exclude)

phtest(base_eu_mean, base_eu_re)
```
Results of Hausman test:
p-value < 0.05
Alternative hypothesis: one model is inconsistent
Use fixed effects

# Creating Sample Subset - with CPP Only  
```{r}
library(dplyr)
cppeu8 <- cppeu7 %>% filter (NumberCPP == 1)

```

# Regression of Sample Subset
```{r}
library(stargazer)

sub_eu_mean<- plm(Price~mean_iso_d +  mean_region + mean_global + logGDPmillions +logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2, data = cppeu8, index = "ifs", model = "within", na.action=na.exclude)

sub_eu_max<- plm(Price~max_iso_d + mean_region + mean_global + logGDPmillions +logGDP_PCthousands  + renewable + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2, data = cppeu8, index = "ifs", model = "within", na.action=na.exclude)

sub_eu_min<- plm(Price~min_iso_d + mean_region + mean_global + logGDPmillions +logGDP_PCthousands  + renewable + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu8, index = "ifs", model = "within", na.action=na.exclude)

EUsub <- stargazer(sub_eu_mean, sub_eu_max, sub_eu_min,
          type = "html",
          title = "EU Model- Neighbourhood Effect on Price of CPP (subset of results with Price >0)",
          dep.var.labels = "CPP Price in Constant US Dollars",
          column.labels = c("Mean Price", "Maximum Price", "Minimum Price"),
          covariate.labels = c("Mean Carbon Price, Neighbours", "Maximum Carbon Price, Neighbours", "Minimum Carbon Price, Neighbours", "Regional Mean Price", "Global Mean Price", "GDP (Millions, Logged)", "GDP Per Capita (Thhousands, Logged)", "Renewable Energy Consumption (% of total)",  "Trade (% of GDP)", "CO2 emissions (Metric Tons Per Capita, Logged )","Natural Resource Rents (% of GDP)", "Population (Thousands, Logged)", "Check and Balances (DPI Index)"),
          style = "apsr", notes.append = TRUE, notes.align = "c",
          notes.label = 'Notes:',
          notes ="\\parbox[t]{\\textwidth}{CCarbon Prices are those of a country's Immediate Neighbours}",
          no.space=TRUE,
          out = "EUsub.htm")
# Note that the lines above create a html file in your working directory with the regression output
```

# Lagging Price 
```{r}
library("dplyr") 
cppeu7$ifs <- as.character(cppeu7$ifs)

# 1 Year Lag
cppeu7 <- cppeu7 %>%                          
  group_by(ifs) %>%
  dplyr::mutate(PriceLagged = dplyr::lag(Price, n = 1, default = NA)) %>% 
  as.data.frame()
      
# 2 Year Lag
cppeu7 <- cppeu7 %>%                          
  group_by(ifs) %>%
  dplyr::mutate(PriceLagged2 = dplyr::lag(Price, n = 2, default = NA)) %>% 
  as.data.frame()

# 3 Year Lag
cppeu7 <- cppeu7 %>%                          
  group_by(ifs) %>%
  dplyr::mutate(PriceLagged3 = dplyr::lag(Price, n = 3, default = NA)) %>% 
  as.data.frame()

# 4 Year Lag
cppeu7 <- cppeu7 %>%                          
  group_by(ifs) %>%
  dplyr::mutate(PriceLagged4 = dplyr::lag(Price, n = 4, default = NA)) %>% 
  as.data.frame()

# 5 Year Lag
cppeu7 <- cppeu7 %>%                          
  group_by(ifs) %>%
  dplyr::mutate(PriceLagged5 = dplyr::lag(Price, n = 5, default = NA)) %>% 
  as.data.frame()

# 10 Year Lag
cppeu7 <- cppeu7 %>%                          
  group_by(ifs) %>%
  dplyr::mutate(PriceLagged10 = dplyr::lag(Price, n = 10, default = NA)) %>% 
  as.data.frame()

# 15 Year Lag
cppeu7 <- cppeu7 %>%                          
  group_by(ifs) %>%
  dplyr::mutate(PriceLagged15 = dplyr::lag(Price, n = 15, default = NA)) %>% 
  as.data.frame()
```

# Regression of Lagged Prices against Mean Neighbour Prices
```{r}
base_eu_mean<- plm(Price~mean_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag1_eu_mean<- plm(PriceLagged~mean_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag2_eu_mean<- plm(PriceLagged2~mean_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag3_eu_mean<- plm(PriceLagged3~mean_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag4_eu_mean<- plm(PriceLagged4~mean_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag5_eu_mean<- plm(PriceLagged5~mean_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag10_eu_mean<- plm(PriceLagged10~mean_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag15_eu_mean<- plm(PriceLagged15~mean_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

EUmeanlag <- stargazer(base_eu_mean, lag1_eu_mean, lag2_eu_mean,lag3_eu_mean,lag4_eu_mean,lag5_eu_mean,lag10_eu_mean, lag15_eu_mean,
          type = "html",
          title = "EU Model - Neighbourhood Effect (Mean Prices) on Lagged Price of CPP",
          dep.var.labels = "CPP Price in Constant US Dollars",
          column.labels = c("No Lag", "One-Year Lag", "Two-Year Lag", "Three-Year Lag", "Four-Year Lag", "Five-Year Lag", "10-Year Lag", "15-Year Lag"),
          covariate.labels = c("Mean Carbon Price, Neighbours", "Regional Mean Price","Global Mean Price by Year", "GDP (Millions, Logged )", "GDP Per Capita (Thousands, Logged )", "Renewable Energy Consumption (% of total)",  "Trade (% of GDP)", "CO2 emissions (Metric Tons Per Capita), Logged ","Natural Resource Rents (% of GDP)", "Population (Thousands, Logged)", "Check and Balances (DPI Index)"),
          style = "apsr", notes.append = TRUE, notes.align = "c",
          notes.label = 'Notes:',
          notes ="\\parbox[t]{\\textwidth}{Carbon Prices are those of a country's Immediate Neighbours}",
          no.space=TRUE,
          out = "EUmeanlag.htm")
# Note that the lines above create a html file in your working directory with the regression output
```

#Regression of Lagged Prices against Max Neighbour Prices
```{r}
base_eu_max<- plm(Price~max_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag1_eu_max<- plm(PriceLagged~max_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag2_eu_max<- plm(PriceLagged2~max_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag3_eu_max<- plm(PriceLagged3~max_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag4_eu_max<- plm(PriceLagged4~max_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag5_eu_max<- plm(PriceLagged5~max_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag10_eu_max<- plm(PriceLagged10~max_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

lag15_eu_max<- plm(PriceLagged15~max_iso_d + mean_region + mean_global + logGDPmillions + logGDP_PCthousands + renewable  + trade_gdp + logCO2_PC +  lognatural_resource_gdp + logpopulationby1000  + checks2 , data = cppeu7, index = "ifs", model = "within", na.action=na.exclude)

EUmaxlag <- stargazer(base_eu_max, lag1_eu_max, lag2_eu_max,lag3_eu_max,lag4_eu_max,lag5_eu_max,lag10_eu_max,lag15_eu_max,
          type = "html",
          title = "EU Model - Neighbourhood Effect (Max Prices) on Lagged Price of CPP",
          dep.var.labels = "CPP Price in Constant US Dollars",
          column.labels = c("No Lag", "One-Year Lag", "Two-Year Lag", "Three-Year Lag", "Four-Year Lag", "Five-Year Lag", "10-Year Lag", "15-Year Lag"),
          covariate.labels = c("Max Carbon Price, Neighbours", "Regional Mean Price","Global Mean Price by Year", "GDP (Millions, Logged)", "GDP Per Capita (Thousands, Logged)", "Renewable Energy Consumption (% of total)",  "Trade (% of GDP)", "CO2 emissions (Metric Tonnes Per Capita, Logged)","Natural Resource Rents (% of GDP)", "Population (Thousands, Logged )", "Check and Balances (DPI Index)"),
          style = "apsr", notes.append = TRUE, notes.align = "c",
          notes.label = 'Notes:',
          notes ="\\parbox[t]{\\textwidth}{Carbon Prices are those of a country's Immediate Neighbours}",
          no.space=TRUE,
          out = "EUmaxlag.htm")
# Note that the lines above create a html file in your working directory with the regression output
```

